More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-09-28 2016-Weak-FH-Bisim/WeakBisim.tex

%\def\Talg{\mathcal{T}_{\Sigma}}
%\def\BoolExprs{\mathcal{B}}
%\def\Exprs{\mathcal{E}} \TODO{use Exprs}
%\def\Actionalg{\mathcal{A}}

@@

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {\alpha} s'}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
 \begin{mathpar}
%    \left( fresh \ \overline{\alpha_i}, \overline{b_j}, v_x.\ \
    \openrule
         {
           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTarrow {\alpha_x} t_x}
%         \right)
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred_{s,t} \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. \beta_j=\beta_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.

@@

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {\alpha} s'}

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, \{j\in J_1|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j\in J_x. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

@@

\begin{lemma} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \bigvee\\   
 \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)  \Longleftrightarrow  {
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
}
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
\displaystyle{\overline{\gamma}=\mybigdotcup_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\overline{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}\\
\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
$

@@

\item Similarly, a series of $m_1=n+m+1$  open transitions can be simplified: 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \overline{\gamma_3},\Pred_3,\Post_3   }
         {s_2 \OTWeakarrow {\tau} s'} \in\! \WT
\bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots m_1].\openrule
    {
       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where\\
$
s_2=s^3_0 \wedge s^1_{m_1}=s',
\displaystyle{\overline{\gamma_3}=\mybigdotcup_{i=0}^{m_1} \vis{\overline{\beta^3_i}}},
\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred^3_i,\Post_3\!=\! \biguplus_{i=0}^{m_1} \Post_i^3\\
$

\item On the other hand, by induction hypothesis we have:
\begin{mathpar}
\bigg(\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT\bigg)
\Rightarrow
\Bigg(\forall i \in [0\ldots n_2].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}  \wedge

\openrule
         {
           \overline{\beta^2},\Pred^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
 \wedge
\forall i \in [0\ldots m_2].\openrule
         {
           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)         
\end{mathpar}
where\\
$
s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2,
\displaystyle{\overline{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}}  \mybigdotcup_{i=0}^{m_2} \vis{\overline{\beta^3_i}}}
\\
\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
\\
\Post_2= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}
$
\end{enumerate}
~~\\
Therefore, we can deduce that:
\begin{mathpar}
\bigg( { \openrule
         {
           \overline{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}\bigg)
 \Rightarrow
\Bigg(\forall i\in [0\ldots(n_1\!+\!n_2)].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in\mathcal{T} \wedge

\openrule
         {
           \overline{\beta^2},\Pred^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\wedge
\forall i \in [0\ldots(m_1\!+\!m_2)].\openrule
         {\overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i\OTarrow {\tau} s^3_{i+1}}\in\mathcal{T}\Bigg)  
\end{mathpar}

where\\
\[
\begin{array}{l}
s_1\!=\!s^1_0 \wedge s^1_{n_1+n_2}\!=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_1+m_2}\!=\!s'\\
\displaystyle{\overline{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\overline{\beta^1_i}}
\dotcup\vis{\overline{\beta^2}}\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\vis{\overline{\beta^3_i}}
}\\
\displaystyle{\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}}
\\
\displaystyle{\Post= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}}
\end{array}
\]
\end{itemize}

>>>>

%\def\Talg{\mathcal{T}_{\Sigma}}
%\def\BoolExprs{\mathcal{B}}
%\def\Exprs{\mathcal{E}} \TODO{use Exprs}
%\def\Actionalg{\mathcal{A}}
\TODO{Attention: la notation of term algebra is the same for set of transition.}

@@

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{j\in J'},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {\alpha} s'}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
 \begin{mathpar}
%    \left( fresh \ \overline{\alpha_i}, \overline{b_j}, v_x.\ \
    \openrule
         {
           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTarrow {\alpha_x} t_x}
%         \right)
\end{mathpar}
 such that  $\forall x, J'=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred_{s,t} \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. \beta_j=\beta_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.

@@

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{j\in J'},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {\alpha} s'}

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j\in J_x. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

@@

\TODO{Lemma revu mais convaincant...}

\begin{lemma} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  \\
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
There exist  sets of $\beta^1_i$, $\beta^2_i$, and $\beta^3_i$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\Bigg(\forall i \in [0\ldots n].\openrule
    {
       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \overline{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg)        
       \bigvee\\   
 \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
 \end{mathpar}
If only if there exist a set of $\beta$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \overline{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
%}
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
\displaystyle{\overline{\gamma}=\mybigdotcup_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\overline{\beta^3_i}}}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}\\
\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
$

@@

\item Similarly, a series of $m_1=n+m+1$  open transitions can be simplified: 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \overline{\gamma_3},\Pred_3,\Post_3   }
         {s_2 \OTWeakarrow {\tau} s'} \in\! \WT
\bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots m_1].\openrule
    {
       \overline{\beta^2_i},\Pred^2_i,\Post^2_i   }
         {s^2_i \OTarrow {\tau} s^2_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where\\
$
s_2=s^2_0 \wedge s^2_{m_1}=s',
\displaystyle{\overline{\gamma_2}=\mybigdotcup_{i=0}^{m_1} \vis{\overline{\beta^2_i}}},
\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred^2_i,\Post_2\!=\! \biguplus_{i=0}^{m_1} \Post_i^2\\
$

\item On the other hand, by induction hypothesis we have:
\begin{mathpar}
\bigg(\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT\bigg)
\Rightarrow
\Bigg(\forall i \in [0\ldots n_2].\openrule
    {
       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}  \wedge

\openrule
         {
           \overline{\beta^4},\Pred^4,\Post^4 }
         {s^4 \OTarrow {\alpha} s'^4} \in \mathcal{T}
 \wedge
\forall i \in [0\ldots m_2].\openrule
         {
           \overline{\beta^5_i},\Pred^5_i,({x^5_k\gets e^5_k})^{k\in K}    }
         {s^5_i \OTarrow {\tau} s^5_{i+1}} \in \mathcal{T}
\Bigg)         
\end{mathpar}
where\\
$
s_1=s^3_0 \wedge s^3_{n_2}=s^4 \wedge s'^4 = s^5_0 \wedge s^5_{m_2}=s_2,
\displaystyle{\overline{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\overline{\beta^3_i}} \dotcup  \vis{\overline{\beta^4}}  \mybigdotcup_{i=0}^{m_2} \vis{\overline{\beta^5_i}}}
\\
\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^3_i\land\Pred\,^4\subst{ \biguplus_{i=0}^{n_2}\Post^3_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^5_i\subst{\Post^4}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
\\
\Post_2= ({x^5_k\gets (e^5_k\subst {\Post^4})\subst{\biguplus_{i=0}^{n_2} \Post^3_i}})^{k\in K}
$
\end{enumerate}
~~\\
Therefore, we can deduce that:
\begin{mathpar}
\bigg( { \openrule
         {
           \overline{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}\bigg)
 \Rightarrow
\Bigg(\forall i\in [0\ldots(n_1\!+\!n_2)].\openrule
    {
       \overline{\beta^6_i},\Pred^6_i,\Post^6_i   }
         {s^6_i \OTarrow {\tau} s^6_{i+1}} \in\mathcal{T} \wedge

\openrule
         {
           \overline{\beta^7},\Pred^7,\Post^7 }
         {s^7 \OTarrow {\alpha} s'^7} \in \mathcal{T}
\wedge
\forall i \in [0\ldots(m_1\!+\!m_2)].\openrule
         {\overline{\beta^8_i},\Pred^8_i,({x^8_k\gets e^8_k})^{k\in K}    }
         {s^8_i\OTarrow {\tau} s^8_{i+1}}\in\mathcal{T}\Bigg)  
\end{mathpar}

such that\\
$
s_i^6= \left\{
 \begin{array}{ll}
s_i^1 & \mbox{if }i<n_1\\
s_{i-n_1}^3 & \mbox{if }i\geq n_1\\
\end{array}
\right. \, \wedge \,
s_i^8= \left\{
 \begin{array}{ll}
s_i^2 & \mbox{if }i<m_1\\
s_{i-m_1}^5 & \mbox{if }i\geq m_1\\
\end{array}
\right. \\
s\!=\!s^6_0 \wedge s^6_{n_1+n_2}\!=s^7 \wedge s'^7 = s^8_0 \wedge s^8_{m_1+m_2}\!=\!s'\\
~~\\
\displaystyle{\overline{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2}\!\! \vis{\overline{\beta^6_i}}
\dotcup\vis{\overline{\beta^7}}\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\overline{\beta^8_i}}
}\\
\displaystyle{\Pred=\bigwedge_{i=0}^{n_2}\Pred^6_i\land\Pred^7\subst{ \biguplus_{i=0}^{n_2}\Post^6_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred^6_i\subst{\Post^7}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^6_i}}
\\
\displaystyle{\Post= ({x^8_k\gets (e^8_k\subst {\Post^7})\subst{\biguplus_{i=0}^{n_2} \Post^6_i}})^{k\in K}}
$
\end{itemize}
